---
title: "R Notebook"
output: html_notebook
---

Click the green triangle on the top right of the cell to run the code:

```{r}
library(sf)
library(osmdata)
library(magrittr)
library(dplyr)
library(ggplot2)
```

This next cell loads geographic data for pubs, streets, and canals in Leiden. 

You can change out the key and value entries to basically anything available here: https://wiki.openstreetmap.org/wiki/Map_features. 

You can also choose another geographic area. Create a bounding box using the tool here: https://boundingbox.klokantech.com/. Under the 'copy and paste' at the bottom-left, choose the 'csv' option. Paste the numbers here in place of the numbers between the `c()` at the beginning of the next cell.



```{r}

box = c(4.476609,52.149951,4.511228,52.168014)

pubs = opq(bbox = c(box[1],box[2],box[3],box[4])) %>%
    add_osm_feature(key = 'amenity', value = 'pub')%>%
    osmdata_sf ()

streets = opq(bbox = c(box[1],box[2],box[3],box[4])) %>%
    add_osm_feature(key = 'highway', value = 'residential')%>%
    osmdata_sf ()

canals = opq(bbox = c(box[1],box[2],box[3],box[4])) %>%
    add_osm_feature(key = 'waterway', value = 'canal')%>%
    osmdata_sf ()

pubs_sf = pubs$osm_points %>% st_set_crs(4326)
streets_sf = streets$osm_lines %>% st_set_crs(4326)
canals_sf = canals$osm_lines %>% st_set_crs(4326)

```

This final cell draws a simple map. You can change the colours by swapping in different text, and make many other changes. 

```{r}
ggplot() + 
  geom_sf(data = pubs_sf, color = 'red') + 
  geom_sf(data = canals_sf, color = 'lightblue', lwd = 2) + 
  geom_sf(data = streets_sf, color = 'black') + 
  coord_sf(xlim = c(box[1], box[3]), ylim = c(box[2],box[4])) + 
  theme_void()
```

